Neighbor-Based Decentralized Training Strategies for Multi-Agent Reinforcement Learning

### 2024-10-04 paper-2024-sac-marl-neighbouring-strategies.tex
add learning algorithm description

% Specify the chosen RL algorithm (DQN) and its hyperparameter configuration
\subsection{Learning algorithm}

% Define the evaluation metrics: average episode length and average reward
\subsection{Evaluation metrics} 
In our experiments, we employed two metrics to evaluate the performance of the learning
  agents and monitor the quality of the training process, namely: 
  \begin{enumerate*}[label=(\roman*)]
    \item \emph{Mean Episode Reward}; and
    \item \emph{Mean Episode Length}.
  \end{enumerate*}

>>>>

\subsection{Learning algorithm}
In our experiments, we employed the well-known \emph{Deep Q-Learning} (DQN) algorithm implemented in RLlib.
%
We set the discount factor $\gamma$ to $0.95$, this parameter controls how much future rewards are 
  considered in the decision-making process.
%
A value slightly below $1$ encourages the agent to prioritize immediate rewards while still accounting 
  for long-term benefits, striking a balance between short-term and long-term planning.
%
We chose a learning rate of $0.001$ to control the speed at which the Q-network's weights are updated.
%
This relatively low learning rate ensures stable learning, preventing large updates that could destabilize 
  the training process, specially in complex environments with multiple interacting agents.
%
For the training batch size, we used a value of $32$, which balances computational efficiency and the diversity 
  of experiences in each update. 
%
A smaller batch size could lead to noisier updates, while a larger one might slow down training without
  significantly improving performance.
%
Additionally, we enabled two key features of the DQN algorithm, namely:
  \begin{enumerate*}[label=(\roman*)]
    \item \emph{Double Q-Learning}, to mitigate the overestimation bias that traditional Q-Learning algorithms are prone to. 
      This is particularly important in multi-agent settings, where overestimation can lead to suboptimal policies due to 
      the complex interactions between agents ; and
    \item \emph{Dueling Q-Learning}, which separates the estimation of the state value from the state-dependent action advantages, 
      enabling the agent to better distinguish between the value of being in a given state and the value of choosing 
      specific actions within that state.
  \end{enumerate*}

\subsection{Evaluation metrics} 
In our experiments, we employed two metrics to evaluate the performance of the learning
  agents and monitor the quality of the training process, namely: 
  \begin{enumerate*}[label=(\roman*)]
    \item \emph{Mean Episode Reward}; and
    \item \emph{Mean Episode Length}.
  \end{enumerate*}
